SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
minor fixes

Cross-site scripting attacks fall into two categories, {\it non-persistent}
(also known as \emph{reflected}) {\sc xss}
and {\it persistent} (also known as \emph{stored}) {\sc XSS}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.

Cross-site request forgery attacks typically involve just a
URL or page that contains a malicious request towards
a site vulnerable to {\sc csrf}.
An attacker can entice a victim to click on the URL or visit the page
through social engineering ({\sc csrf} 1), which will the result in a malicious
request towards the vulnerable site ({\sc csrf} 2).
Note that this scenario does not involve the injection of any code through the
exploitation of some server-side vulnerability (as is the case with Server 1).
On the other hand, {\sc csrf} is also possible through injection
({\sc i-csrf}). In this attack, an attacker
manages to inject {\sc html} code that contains
a malicious {\sc csrf} request in the way we described in
Section~\ref{sec:attacks}.
This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application when
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser, a malicious request will be generated
towards the site that is vulnerable to {\sc csrf}.

>>>>

Cross-site scripting attacks fall into two categories, {\it non-persistent}
(also known as \emph{reflected}) {\sc xss}
and {\it persistent} (also known as \emph{stored}) {\sc xss}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.

Cross-site request forgery attacks typically involve just a
{\sc url} or page that contains a malicious request towards
a site vulnerable to {\sc csrf}.
An attacker can entice a victim to click on the {\sc url} or visit the page
through social engineering ({\sc csrf} 1), which will the result in a malicious
request towards the vulnerable site ({\sc csrf} 2).
Note that this scenario does not involve the injection of any code through the
exploitation of some server-side vulnerability (as is the case with Server 1).
On the other hand, {\sc csrf} is also possible through injection
({\sc i-csrf}). In this attack, an attacker
manages to inject {\sc html} code that contains
a malicious {\sc csrf} request in the way we described in
Section~\ref{sec:attacks}.
This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application when
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser, a malicious request will be generated
towards the site that is vulnerable to {\sc csrf}.
